Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2019-11-13 paper2_JNLS/paper.tex
minor changes

\todo[inline]{Di, I do not understand this paragraph. Is the $F$ meant to be the same $F$ as above, i.e.~the right-hand-side of the TKdV equation \eqref{TKdV2}? Or is $F$ some arbitrary function of the state variable that we want to compute the expectation of?}
Then the PDFs can be counted from the solution $\uL(t)$, and the statistical expectations can be calculated by averaging along the trajectory
\begin{equation}
\left\langle F \left(u_{\Lambda}\right)\right\rangle _{\mu}=\frac{1}{T}\int_{t_{0}}^{t_{0}+T} F \left(u_{\Lambda}\left(t\right)\right)dt,
\end{equation}
given ergodicity in the solution with $\uL(t_0)$ already reaching the stationary state.

>>>>

\todo[inline]{Di, I do not understand this paragraph. Is the $F$ meant to be the same $F$ as above, i.e.~the right-hand-side of the TKdV equation \eqref{TKdV2}? Or is $F$ some arbitrary function of the state variable that we want to compute the expectation of? 
$F$ should be some arbitrary function for the expectation.}
Then the PDFs can be counted from the solution $\uL(t)$, and the statistical expectation of any functional $f$ can be calculated by averaging along the trajectory
\begin{equation}
\left\langle f \left(u_{\Lambda}\right)\right\rangle _{\mu}=\frac{1}{T}\int_{t_{0}}^{t_{0}+T} f \left(u_{\Lambda}\left(t\right)\right)dt,
\end{equation}
given ergodicity in the solution with $\uL(t_0)$ already reaching the stationary state.
